What is the Effect of X on Y?

### 2023-10-26 latex-article/article.tex
Updated article template
Clean up title page
Update tables for slides

\title{Example Paper}
\author{
  Author One%
  \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.} \ and Author Two%
  \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.}
}
\date{\today}

% Conditionally include comments. Switch to \togglefalse
\newtoggle{INCLUDECOMMENTS}
\toggletrue{INCLUDECOMMENTS}
% \togglefalse{INCLUDECOMMENTS}
\newcommand{\kyle}[1]{\iftoggle{INCLUDECOMMENTS}{
  \orange{\textbf{Kyle:} #1}
}{}}

\hfuzz=100pt

@@

\texttt{\textbackslash P}, \texttt{\textbackslash prob}, \texttt{\textbackslash cov}, and \texttt{\textbackslash var} work the same way too:
$$\P \quad \P[i] \quad \P{X_i} \quad \P[i]{D_i} \quad \P{\bar{X}_n > \bar{X}}{\mu = \mu_0} \quad \P[\mathcal{F}]{X_i}{D_i = 1}$$
$$\cov{X_n, Y_n} \quad \var[i](\bar{X}_n)$$

\texttt{\textbackslash one} does an indicator. Same as above, but no conditional:
$$\one{X_i > 0}$$

We have \texttt{\textbackslash aslim}, \texttt{\textbackslash plim}, and \texttt{\textbackslash convd} for convergence symbols. There's also \texttt{\textbackslash iid}. Examples:
$$\bar{x}_n \aslim \mu \quad \bar{x}_n \plim \mu \quad \bar{x}_n \convd N(0, 1)$$
$$X_i \iid N(0, 1)$$

@@

For tables, I use the \texttt{tabular} and \texttt{booktabs} packages. For table and figure notes, I use a custom \texttt{\textbackslash note} command. It uses \texttt{\textbackslash parbox} under the hood. You can use it in one of of four ways:
\begin{enumerate}
  \item \texttt{\textbackslash note\{text\}}
  \item \texttt{\textbackslash note[Notes.]\{text\}}
  \item \texttt{\textbackslash note\{0.6\textbackslash textwidth\}\{text\}}
  \item \texttt{\textbackslash note[Notes.]\{0.6\textwidth\}\{text\}}
\end{enumerate}

@@

      % Body
      \input{summary.tex}

@@

  \note{Weekly wage is reported in 2015 \$.}
\end{table}

>>>>

\title{Example Paper\thanks{\acknlowledgements}}
\author{
  Author One\thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.} 
  \ and 
  Author Two\thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.}
}
\date{\textsc{\today}}
\def\acknlowledgements{%
  Acknlowedgements
}

% Conditionally display thoughts (hide by switching to `\boolfalse`)
\booltrue{INCLUDECOMMENTS}
\newcommand{\kyle}[1]{\coauthorComment[Kyle]{#1}}

@@

\texttt{\textbackslash P}, \texttt{\textbackslash prob}, \texttt{\textbackslash cov}, and \texttt{\textbackslash var} work the same way too:
$$\P \quad \P[i] \quad \P{X_i} \quad \P[i]{D_i} \quad \P{\bar{X}_n > \bar{X}}{\mu = \mu_0} \quad \P[\mu]{X}{D = 1}$$
$$\cov{X_n, Y_n} \quad \var[i](\bar{X}_n)$$

\texttt{\textbackslash one} does an indicator. Same as above, but no conditional:
$$\one{X_i > 0} \quad (Y_i, D_i) \indep X_i$$

We have \texttt{\textbackslash asto}, \texttt{\textbackslash pto}, and \texttt{\textbackslash dto} for convergence symbols:
$$\bar{x}_n \asto \mu \quad \bar{x}_n \pto \mu \quad \bar{x}_n \dto N(0, 1)$$

There's also \texttt{\textbackslash iid} and \texttt{\textbackslash plim} for the probability limit operator:
$$\plim_{n\to \infty} \frac{1}{n} X' X = S_{X'X} \quad X_i \iid N(0, 1)$$

@@

For tables, I use the \texttt{tabular} and \texttt{booktabs} packages. For table and figure notes, I use a custom \texttt{\textbackslash note} command. It uses \texttt{\textbackslash parbox} under the hood. You can use it in one of of four ways:
\begin{enumerate}
  \item \texttt{\textbackslash note\{text\}}
  \item \texttt{\textbackslash note[Notes.]\{text\}}
  \item \texttt{\textbackslash note\{0.6\textbackslash textwidth\}\{text\}}
  \item \texttt{\textbackslash note[Notes.]\{0.6\textbackslash textwidth\}\{text\}}
\end{enumerate}

@@

      % Body
      \input{tables/summary.tex}

@@

  \note{Weekly wage is reported in 2015.}
\end{table}

### 2023-10-26 latex-slides/slides.tex
Add \orange to slides
Update tables for slides

\documentclass[aspectratio=169,t,11pt]{beamer}
% \documentclass[aspectratio=43,t,11pt]{beamer}
\usepackage{slides,math}

% Define `accent`/`accent2` colors for theme customization
\definecolor{accent}{HTML}{006896}
\definecolor{accent2}{HTML}{695693}

@@

  \bottomleft{\hyperlink{appendix1}{\beamergotobutton{Appendix}}}
\end{frame}

@@

@@

\begin{frame}{Components}{Background Colors}
  \bgNavy{Test word} with \textbackslash bgNavy\{...\}

  \bgPurple{Test word} with \textbackslash bgPurple\{...\}

  \bgOrange{Test word} with \textbackslash bgOrange\{...\}

  \bgTeal{Test word} with \textbackslash bgTeal\{...\}

  \bgKelly{Test word} with \textbackslash bgKelly\{...\}

  \bgRuby{Test word} with \textbackslash bgRuby\{...\}

  \bgAlice{Test word} with \textbackslash bgAlice\{...\}

  \bgDaisy{Test word} with \textbackslash bgDaisy\{...\}

  \bgCoral{Test word} with \textbackslash bgCoral\{...\}

  \bgCranberry{Test word} with \textbackslash bgCranberry\{...\}
\end{frame}

@@

\begin{frame}{Components}{Two Columns with Figure}
  \begin{columns}[T]
  \vspace{0pt}
  \begin{column}{.5\textwidth}
    \includegraphics[width=\textwidth]{img/kanagawa.jpg}
  \end{column}
  \hfill
  \begin{column}{.48\textwidth}
    \begin{itemize}
    \item A point about the figure that is potentially important.
    \item Another point about the figure that is also potentially important.
    \end{itemize}
  \end{column}
  \end{columns}
\end{frame}

@@

@@

        \only<1>{
          Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
          &  (0.149) & (0.129) \\
        }
        \only<2>{
          \marktopleft{ex1}Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
          &  (0.149) & (0.129) \markbottomright{ex1} \\
        }
        No Special Privileges & -0.104 & $-$0.103  \\ 
        & (0.135) & (0.129) \\
        Opportunity to Learn & 0.249 & 0.238$^{*}$ \\ 
        & (0.160) & (0.139) \\

@@

  \begin{itemize}
  \item Ideally, your figure is the same aspect as the frame \texttt{4:3} or \texttt{16:9} or else there will be white space in one of the directions.
  \end{itemize}
\end{frame}

\begin{frame}{Figure}{}
  \begin{adjustbox}{width = 0.7\textwidth, center}
  \includegraphics{img/kanagawa_16_9.png}
  \end{adjustbox}
\end{frame}

@@

    \note{0.8\textwidth}{Using R base dataframe \texttt{attitude}. R base dataframe attitude. R base dataframe attitude.}
  \end{table}

  \bottomleft{\hyperlink{main1}{\beamerreturnbutton{Back}}}
  % \bottomright{\hyperlink{main1}{\beamerreturnbutton{Back}}}
\end{frame}

>>>>

\documentclass[aspectratio=169,t,11pt,table]{beamer}
\usepackage{slides,math}
% \geometry{paperwidth=168mm,paperheight=94.5mm}

% Define `accent`/`accent2` colors for theme customization
% I recommend changing the top slider on this: 
% https://hslpicker.com/#1e9400
\definecolor{accent}{HTML}{006896}
\definecolor{accent2}{HTML}{940034}

@@

  \bottomleft{
    \hyperlink{appendix1}{\beamergotobutton{Appendix}}
    \beamergotobutton{Button 2} 
    \beamergotobutton{Button 3}
  }
\end{frame}

@@

  \orange{Test sentence with \textbackslash orange\{...\}}

@@

@@

\begin{frame}{Components}{Two Columns with Figure}
  \begin{columns}[T]
    \begin{column}{.54\textwidth}
      \includegraphics[width=\textwidth]{img/kanagawa.jpg}
    \end{column}
    \hfill
    \begin{column}{.46\textwidth}
      \begin{itemize}
      \item A point about the figure that is potentially important.
      \item Another point about the figure that is also potentially important.
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}{Table with cell / row highlighting}{}
  Use \texttt{\textbackslash cellcolor<\#>\{color\}} and \texttt{\textbackslash rowcolor<\#>\{color\}} to color cell / row. The \texttt{<\#>} is an optional overlay specification

  \medskip
  \begin{table}[h]
    \centering
    \begin{tabular}{lc}
      \toprule
      & (1) \\
      \midrule
      \rowcolor<2>{alice!15!white}Treatment dummy & \cellcolor<1>{accent!15!white} 0.0694* \\
      \rowcolor<2>{alice!15!white}& (0.0401) \\
      \rowcolor<3>{alice!15!white} Constant & -1.2238*** \\
      \rowcolor<3>{alice!15!white} & (0.0764)  \\
      \hline
      Observations & 1,673  \\
      R-squared & 0.0401 \\

      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}

@@

        \only<1>{
          \marktopleft{ex1}Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
          &  (0.149) & (0.129) \markbottomright{ex1} \\
        }
        \only<2>{
          Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
          &  (0.149) & (0.129) \\
        }
        No Special Privileges & -0.104 & $-$0.103  \\ 
        & (0.135) & (0.129) \\
        Opportunity to Learn & 0.249 & 0.238$^{*}$ \\ 
        & (0.160) & (0.139) \\

@@

  \begin{itemize}
  \item Ideally, your figure is the same aspect as the frame (\texttt{4:3} or \texttt{16:9}) or else there will be white space in one of the directions.
  \end{itemize}
\end{frame}

\begin{frame}{Figure}{}
  The \texttt{adjustbox} environment helps resize figures/tables

  \medskip
  \begin{adjustbox}{width = 0.7\textwidth, center}
    \includegraphics{img/kanagawa_16_9.png}
  \end{adjustbox}
\end{frame}

@@

    \note{0.8\textwidth}{Using R base dataframe \texttt{attitude}. I use my custom \texttt{\textbackslash note} command for notes}
  \end{table}

  \bottomleft{
    \hyperlink{main1}{\beamerreturnbutton{Back}}}
  % \bottomright{\hyperlink{main1}{\beamerreturnbutton{Back}}}
\end{frame}
